---
title: "Prediction Project"
author: "Angelicaqj"
date: "5/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 8,fig.height = 5)
library(MASS)
library(boot)
library(leaps)
library(reshape2)
library(ggpubr)
```


Predicting crime rates in Boston data. The Boston data set is in the MASS package, and first you will need to load it.

```{r}
?Boston # explore the data
head(Boston)
```

Build a regression model to predict the crime rate (crim) in Boston suburbs based on the other provided variables.

The solution includes:

• A brief exploratory analysis.


• A description of the set of regression models to be considered.


• A description of how the models were evaluated.


• A summary of one model, based on the analysis, is the best among to be considered.


## Exploratory Analysis


```{r}
#create a matrix with the correlation of each variable
cor_matrix <- round(cor(Boston),2)
melted_cor_matrix <- melt(cor_matrix)

# create a heatmap to visualize the correlation
ggplot(data = melted_cor_matrix, aes(x = Var1, y = Var2, fill = value)) + geom_tile()
```


```{r}
# Three scatter plots 
q1 <- qplot(x = factor(rad), y = crim, data = Boston)
q2 <- qplot(x = black, y = crim, data = Boston)
q3 <- qplot(x = lstat, y = crim, data = Boston)

ggarrange(q1,q2,q3 , ncol = 3, nrow = 1)
```


<p>&nbsp;</p>

Generalize a linear model 

```{r}
glm_boston <- glm(crim ~ ., data = Boston)
summary(glm_boston)
```

The approach that we have been taking in this dataset is to use regression as a way of summarizing relationships between some of the variables in the dataset.

## Set Regression Models and evaluation

Best subset selection by identifying the best model that contain a given number of predictors.

```{r}
# Best subset selection
regfit_full <- regsubsets(crim ~ ., data = Boston, nvmax = 13)
reg_summary <- summary(regfit_full)
#reg_summary

reg_summary$rsq
```

It seems that the $R^2$ statistic increases from 39%, when only one variable is included in the model, to 45%, when all variables are included. As expected, the $R^2$ statistic increases monotonically as more variables are included.


```{r}
which.min(reg_summary$bic)
plot(reg_summary$bic, xlab="Number of Variables", ylab="BIC", type="l")
points(3, reg_summary$bic[3], col="red", cex=2, pch=20)
plot(regfit_full, scale="bic")
```

In the first plot, we see that there are three variables that share a BIC close to -260. These three variables are representing in the second plot as `rad`, `black`, and `lstat`, that contain the lowest BIC.

<p>&nbsp;</p>

```{r}
# Forward Stepwise Selection
regfit_fwd <- regsubsets(crim ~ ., data = Boston, nvmax = 13, method="forward")
summary(regfit_fwd)

# Backward Stepwise Selection
regfit_bwd <- regsubsets(crim ~ ., data = Boston, nvmax = 13, method="backward")
summary(regfit_bwd)
```

We can see that using forward and backward stepwise selection, the best one-variable model contains only `rad`.


```{r}
# coefficients for these three selections
coef(regfit_full, 3)
coef(regfit_fwd, 3)
coef(regfit_bwd, 3)
```

By looking at the coefficients for these three selections, the best one-variable through three-variable models are each identical for best subset and forward selection.


```{r}
# fit the best model with the best predictors
glm_fit_best <- glm(crim ~ rad + black + lstat, data = Boston)

# find avg. squared error with cross validation
cv_err <- cv.glm(Boston, glm_fit_best)

# cross-validation result
cv_err$delta
```


## Summary

The best model according the Best Subset selection and Forward Stepwise selection is a model with three variables. The BIC plot shows noticeable that `rad`, `black`, and `lstat` have the lowest BIC. Concluding, the regression model to predict the crime rate (crim) in Boston suburbs is the following:

$$ {crime}_i = \beta_0 + \beta_1{rad} + \beta_2{black} + \beta_3{lstat} + \epsilon_i$$

Based on the coefficients the final prediction model is the following:

$$ {crime}_i = -0.37 + 0.49{rad} -0.01{black} + 0.21{lstat}$$
```{r}
summary(lm(crim ~ rad + black + lstat, data = Boston))
```

